Optimal coordination - general experiment analysis.

### 2019-07-15 voltagebudget/analysis/exp127_analysis.Rmd
Add analysis to match last exp change for 127

```{r, message=FALSE}
# Sparse
freqs <- c("8")#, "40", "60")
results <- NULL

exp <- "127a_1"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

@@

@@

exp <- "127b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

@@

@@

>>>>

```{r, message=FALSE}
freqs <- c("8")#, "40", "60")
results <- NULL

# Sparse exps
exp <- "127a_1"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_2"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_3"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_4"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

@@

exp <- "127a_6"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_7"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_8"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

@@

# -
# Org dense code
exp <- "127b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

@@

```{r}
results %>% 
  ggplot(aes(x=(V_osc/V_comp), fill=exp)) +
  geom_histogram(bins=12) +
  facet_grid(exp~As, scale="free") +
  theme_classic()
```

@@

```{r}
results %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, shape=exp)) +
  geom_line(size=2, alpha=0.2) +
  geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```
